\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{color}

\begin{document}
\\
\colorbox{yellow}{Hello, may I help you?}
\\
\colorbox{green}{Hello, yes. I need to install an indor light.}
\\
\colorbox{yellow}{Ok, so you have an idea of what you are going to do?}
\\
\colorbox{green}{Yes the purpose of this lighting is to light my child's bedroom.}
\\
\colorbox{green}{Okey, so I need tape of meter, googles, buble level, electric drill with a metal drill, cutting pliers,}
\colorbox{green}{ wire stripper and water pump plier, a  screwdriver, and little hammer.}
\\
\colorbox{yellow}{But it's missing tools. You need a wire, light switch, multimeter and breaker.}
\\
\colorbox{green}{Good can you help me?}
\\
\colorbox{yellow}{Yes you look for a band?}
\\
\colorbox{green}{My friend recommend me Makita.}
\\
\colorbox{yellow}{Ho that a great make, comme here $*d\'eplacement*$ There is a wire. what lenght of wire do you need?}
\\
\colorbox{green}{I think, I need a 15 meter.}
\\
\colorbox{yellow}{Okey, you need wire: red, blue, yellow and green. The light switch, timer or manual?}
\\
\colorbox{green}{It's manual.}
\\
\colorbox{yellow}{But it's most fragile.}
\\
\colorbox{green}{Perhaps, but I need this.}
\\
\colorbox{yellow}{Great, for the multimeter, maybe it would be better to choose a one with a midrange, for your}
\\
\colorbox{yellow}{ personal used.}
\\
\colorbox{green}{Right, but what's the price?}
\\
\colorbox{yellow}{It's at 70 dollars but you have other at 50 however it's less efficient.}
\\
\colorbox{green}{I rest on midrange.}
\\
\colorbox{yellow}{Alright, the breaker it's a 30mA, it's realy good for you.}
\\
\colorbox{green}{Okey, that's great!}
\\
\colorbox{yellow}{I let you go and settle all your materials, if you don't need my help again.}
\\
\colorbox{green}{Thanks you for your help, I don't need it for the moment, good bye.}
\\
\colorbox{yellow}{Good bye, have a nice DIY.}
\\

\end{document}

